Results

### 2024-07-04 analysis_pipeline.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

---
title: "Preregistered Analysis Pipeline"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
# output: pdf_document
bibliography: 
  - "bibliography/references.bib"
---

>>>>

---
title: "Preregistered Analysis Pipeline"
output:
  html_document:
    toc: TRUE
    # toc_float:
    #   collapsed: FALSE
    toc_depth: 3
# output: pdf_document
bibliography: 
  - "bibliography/references.bib"
---

### 2024-07-04 data_prep.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

---
title: "Data Preparation"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: show
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

>>>>

---
title: "Data Preparation"
output:
  html_document:
    toc: TRUE
    # toc_float:
    #   collapsed: FALSE
    toc_depth: 3
    code_folding: show
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

### 2024-07-04 index.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

On this website, you can find the companion material for the paper _Who needs privacy? Exploring the relations between need for privacy and personality_. The paper is currently submitted to the journal Collabra as registered report. The report is based on an [older paper](https://osf.io/m23bn) that was already submitted to Collabra but rejected. This paper now addresses the [feedback from the original submission](reviews.pdf) and considers the original paper a prestudy.

@@

>>>>

On this website, you can find the companion material for the paper _Who needs privacy? Exploring the relations between need for privacy and personality_. The paper published at the journal Collabra as registered report. The report is based on an [older paper](https://osf.io/m23bn) that was already submitted to Collabra but rejected. This paper now addressed the [feedback from the original submission](reviews.pdf) and considers the original paper a prestudy.

@@

Please cite as follows:

Dienlin, T., & Metzger, M. (2024). Who Needs Privacy? Exploring the Relations Between Need for Privacy and Personality. _Collabra: Psychology_, 10(1), 120402. https://doi.org/10.1525/collabra.120402

### 2024-07-04 items.rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

---
title: "Items"
subtitle: "Data-set: Need for Privacy and Personality"
author: "Tobias Dienlin & Miriam Metzger"
date: "2024-04-05"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
      toc_depth: 3
# output:
#   pdf_document:
#     toc: TRUE
#     toc_depth: 1
bibliography: 
  - "bibliography/references.bib"
---

>>>>

---
title: "Items"
subtitle: "Data-set: Need for Privacy and Personality"
author: "Tobias Dienlin & Miriam Metzger"
date: "2024-04-05"
output:
  html_document:
    toc: TRUE
    # toc_float:
    #   collapsed: FALSE
    toc_depth: 2
# output:
#   pdf_document:
#     toc: TRUE
#     toc_depth: 1
bibliography: 
  - "bibliography/references.bib"
---

### 2024-07-04 items_readability.Rmd
deleting large files
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

---
title: "Readability analyses of items"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

@@

```{r data-wrangling}
d <- read_spss("data/Need+for+Privacy_August+16%2C+2021_15.33.sav")
```

>>>>

---
title: "Readability analyses of items"
output:
  html_document:
    toc: TRUE
    # toc_float:
    #   collapsed: FALSE
    toc_depth: 3
    code_folding: hide
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
  # pdf_document:
  #   toc: TRUE
---

@@

### 2024-07-04 manuscript.Rmd
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

documentclass     : "apa6"
# classoption       : "man"
output            : html_document
# output            : papaja::apa6_pdf
# output            : papaja::apa6_word

@@

All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
A list of all items that we were used are reported in the online supplementary material. 
The personality and privacy items were presented in random order, and the sociodemographic questions were asked at the end.
In the online supplementary material we also report all item statistics and their distribution plots.

@@

Looking at the results more broadly, we make five general observations.
First, it makes sense to differentiate different levels of need for privacy.
Many personality traits showed meaningful relations with some dimension, yet no or even opposite relations with others.
To illustrate, whereas more conscientious people desired less psychological privacy and less privacy from other, when asked about privacy in general and privacy from companies they needed more. 
General need for privacy may rather represent a cognitive appraisal, whereas social or psychological privacy might be more experienced-based and psychological. 
In any case, our results argue for a more rather than less nuanced strategy for measuring privacy attitudes.

@@

The data are shared as a scientific use file on AUSSDA [@dienlinNeedPrivacyPersonality2024].

>>>>

documentclass     : "apa6"
# classoption       : "man"
# output            : html_document
output            : papaja::apa6_pdf
# output            : papaja::apa6_word

@@

All items were answered on a 7-point Likert scale ranging from 1 (_strongly disagree_) to 7 (_strongly agree_).[^2] 
A list of all items that we used are reported in the online supplementary material. 
The personality and privacy items were presented in random order, and the sociodemographic questions were asked at the end.
In the online supplementary material we also report all item statistics and their distribution plots.

@@

Looking at the results more broadly, we make five general observations.
First, it makes sense to differentiate different levels of need for privacy.
Many personality traits showed meaningful relations with some dimension, yet no or even opposite relations with others.
To illustrate, whereas more conscientious people desired less psychological privacy and less privacy from other, when asked about privacy in general and privacy from companies they needed more. 
General need for privacy may rather represent a cognitive appraisal, whereas social or psychological privacy might be more experienced-based and psychological. 
In any case, our results argue for a more rather than less nuanced strategy for measuring privacy attitudes.y

@@

The data are shared as a scientific use file on AUSSDA at https://doi.org/10.11587/IC66GC [@dienlinNeedPrivacyPersonality2024].

### 2024-07-04 results.RmD
- removed toc_float as it's not working with Safari - recompiled results so it's displayed correctly

---
title: "Results"
output:
  html_document:
    toc: TRUE
    toc_float:
      collapsed: FALSE
    toc_depth: 2
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---

>>>>

---
title: "Results"
output:
  html_document:
    toc: TRUE
    # toc_float:
    #   collapsed: FALSE
    toc_depth: 3
    code_folding: hide
    df_print: paged
bibliography      : 
  - "bibliography/r-references.bib"
  - "bibliography/references.bib"
---
